\documentclass[a4paper,12pt,oneside]{report}
%\usepackage[Glenn]{fncychap}
\usepackage[Lenny]{fncychap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{float}


%%% Escolha das fontes
% Charter
%\usepackage[charter]{mathdesign}

%%% Combo: Palatino + Helvetica + Courier, com EulerVM para matemática
\usepackage{mathpazo}
\usepackage[scaled=.95]{helvet}
\usepackage{courier}
\linespread{1.05} %%% Palatino needs more spacing.

%%% Idem, mas pxfonts para matemática
%\usepackage{pxfonts}
%\usepackage[scaled=.95]{helvet}
%\usepackage{courier}
%\linespread{1.05} %%% Palatino needs more spacing.

% Outras fontes
%\usepackage{bookman} % Obsoleto, usar Kerkis
%\usepackage{kmath,kerkis}
%\usepackage[urw-garamond]{mathdesign}
%\usepackage[utopia]{mathdesign}
%\usepackage{mathptmx} % Isso se eu quisesse usar com Times!
%\usepackage{mathrsfs}
%\usepackage{eulervm} % Euler iria bem, mas não nesta tese...
%\usepackage{libertine} % Fonte da Wikipedia!

%
% Geometria da página. Sugiro manter estas mesmas margens e 15 cm de espaço de texto.
\usepackage[a4paper,pdftex,top=2.8cm,bottom=4cm,left=3.4cm,right=2.6cm]{geometry}
\textwidth=15.0 true cm

%
% Table of Contents
\setcounter{tocdepth}{2}

\usepackage{sprace}
\usepackage[]{units}
%
% Use isto pros headers


\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancy}

% % tenemos que apagar dedsde aqui para cambiar el formato de capitulo  

%\renewcommand{\chaptermark}[1]{%
%\markboth{\chaptername\ \thechapter.\ #1}{}}

%% E menos espaço ao começar o capítulo
%\usepackage{titlesec}
%\titleformat{\chapter}[display]
%  {\normalfont\rmfamily\huge\mdseries}
%  {\chaptertitlename\ \thechapter}{20pt}{\huge}
%\titlespacing*{\chapter}{0pt}{-20pt}{40pt}

% %  hasta aqui


% Linha Extra
\newcommand{\linha}{\enlargethispage{1\baselineskip}}

% Páginas bonitas
\fancypagestyle{plain}{%
\fancyhf{} % clear all header and footer fields
\fancyfoot[C]{\textit \thepage} % except the center
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}}

\fancypagestyle{fancyplain}{%
\fancyhf{}
\fancyhead[L]{\textit{\leftmark}}
\fancyhead[R]{\textit{\thepage}}
%\fancyfoot[C]{\today} % Use este fancyfoot pros drafts (data no pé da página)!
\fancyfoot[C]{} % Use este fancyfoot (vazio) pra versão final!
\renewcommand{\headrulewidth}{0.6pt}
\renewcommand{\footrulewidth}{0pt}}

%%%%%%%
% Do the hypersetup
%%%%%%%

\hypersetup{pdftitle={Search for a Heavy Resonance in the MET + Jet Final state},
            pdfauthor={David Romero Abad},
            pdfsubject={High Energy Physics},
            pdfkeywords={High Energy Physics}
            			{Particle Physics}
            			{Hadron Colliders} 
				{Extra Dimensions}
				{Beyond the Standard Model},
			colorlinks=true,
			citecolor=blue,
			linkcolor=blue			
            }

\begin{document}

%%% This makes all the frontmatter stuff, sans the Table of Contents.
\pagestyle{plain}

%\input Preambulo.tex
\input{TitlePage/TitlePage.tex}



%\input blanco.tex

\pagenumbering{roman}

\input{Abstract/abstract.tex}

%\input blanco2.tex

%%% The Table of Contents and a new page
\tableofcontents
\newpage

%%%
%%% Ok, ready to start. Reset headings and page numbers.
%%%

\pagenumbering{arabic}



\input{Introduction/Introduction.tex}


\input{Chapter1/cap1.tex}


\input{Chapter2/CMS.tex}

\begin{comment}
\input PhysicsObjects.tex
\input Analysis.tex
\input Conclusions.tex
%\input DataED.tex
%\input Conclusao.tex

%\input cap2.tex
%\input cap3.tex
\appendix
%%% Truque
\renewcommand{\chaptername}%
    {Apêndice}
%\input analise_Zjets.tex
%\input ap1.tex
%\input ap2.tex
%\input ap3.tex
%\bibliography{mibiblio}{}
%\bibliographystyle{unsrtnat}

\begin{thebibliography}{9}

\bibitem{higgsdisco}
CMS Collaboration,
"Observation of a new boson at a mass of 125 GeV with the CMS experiment at the LHC", 
Physics Letters B, Volume 716, Issue 1, 17 September 2012, Pages 30–61.

\bibitem{Randall:1999ee}
Lisa Randall and Raman Sundrum,
"Large Mass Hierarchy from a Small Extra Dimension",
Phys.Rev.Lett. 83.3370 (1999),
\eprint{hep-ph/9905221}.

\bibitem{Randall:1999vf}
Lisa Randall and Raman Sundrum,
An Alternative to Compactification"
Phys. Rev. Lett.83.4690,
\eprint{hep-th/9906064}.

\bibitem{Aga}
Kaustubh Agashe and Hooman Davoudiasl and Gilad Perez and Amarjit Soni,
"Warped Gravitons at the LHC and Beyond",
Phys. Rev. D 76.036006,
\eprint{hep-ph/0701186}.

\bibitem{Fitz}
A. L. Fitzpatrick, J. Kaplan, L. Randall, and L.T. Wang,
"Searching for the Kaluza-Klein Graviton in Bulk RS Models",
JHEP 0709 (2007) 013,
\eprint{hep-ph/0701150}.

\bibitem{HVT}
D. Pappadopulo, A. Thamm, R. Torre, and A. Wulzer, "Heavy Vector Triplets: Bridging Theory and Data", (2014),
\eprint{1402.4431}.

\bibitem{glashow}
S. Glashow,
"Partial-symmetries of weak interactions",
Nucl. Phys. 22 (1961) 579.

\bibitem{weinberg}
S. Weinberg,
"A Model of Leptons",
Phys. Rev. Lett. 19 (1967) 1264.

\bibitem{salam}
A. Salam,
N. Svartholm, ed. Elementary Particle Physics: Relativistic Groups and Analyticity. Eighth Nobel Symposium. Stockholm: Almquvist and Wiksell. p. 367.

\bibitem{higgs}
Peter W. Higgs,
"Spontaneous Symmetry Breakdown without Massless Bosons",
Phys. Rev. 145, 1156  (1966).

\bibitem{goldstone1}
Jeffrey Goldstone, Abdus Salam, and Steven Weinberg,
"Broken Symmetries",
Phys. Rev. 127, 965 (1962).

\bibitem{nambu}
Yoichiro Nambu,
"Axial Vector Current Conservation in Weak Interactions",
Phys. Rev. Lett. 4, 380 (1960).

\bibitem{gold2}
J. Goldstone,
"Field Theories with Superconductor Solutions",
Nuovo Cimento 19: 154–164.

\bibitem{kibble}
T. W. B. Kibble,
"Symmetry Breaking in Non-Abelian Gauge Theories",
Phys. Rev. 155, 1554 (1967).

\bibitem{csaki}
Csaba Csaki,
"TASI Lectures on Extra Dimensions and Branes",
\eprint{hep-ph/0404096v1} (2004)


\bibitem{ArkaniHamed:1998a}
Nima Arkani-Hamed and Savas Dimopoulos and G. R. Dvali
"The Hierarchy problem and new dimensions at a millimeter", 
Phys.Lett. B429 (1998) 263–272, doi:10.1016/S0370-2693(98)00466-3,
arXiv:hep-ph/9803315.

\bibitem{Antoniadis:1998b}
Antoniadis and N. Arkani-Hamed and S. Dimopoulos
\emph{"New dimensions at a millimeter to a Fermi and superstrings at a TeV"}
Phys. Lett.B 436 (1998), arXiv:hep-ph/9804398.

\bibitem{UED}
Thomas Appelquist, Hsin-Chia Cheng, Bogdan A. Dobrescu, 
"Bounds on Universal Extra Dimensions",
Phys.Rev.D64:035002,(2001),
\eprint{hep-ph/0012100}


\bibitem{Goldb}
W. D. Goldberger and M. B. Wise 
\emph{"Phenomenology of a Stabilized Modulus"}
Physics Letters B, Volume 475, Issues 3-4, 2 March 2000, Pages 275-279, arXiv:hep-ph/9911457.

\bibitem{lhc}
Oliver S. Bruning, P. Collier, P. Lebrun, S. Myers, R. Ostojic, J. Poole, P. Proudlock,
"LHC Design Report Vol.1: The LHC Main Ring", CERN-2004-003-V1 (2004).	

\bibitem{HCAL}
  CMS Collaboration,
  \emph{"The Hadron Calorimeter Technical Design Report"},
  CERN/LHCC   97-031 (1997). CMS TDR 2. 
  
\bibitem{HCAL2}  
S. Abdullin et al., \emph{"Design, performance and calibration of the CMS forward calorimeter wedges"}, Eur.Phys.J. C53 (2008) 139–166.

\bibitem{HCAL3}
S. Abdullin et al., \emph{"Design, performance, and calibration of CMS hadron-barrel calorimeter wedges"}, Eur. Phys. J. C55 (2008) 159–171.

\bibitem{HCAL4}
S. Abdullin et al., \emph{"Design, performance, and calibration of the CMS Hadron- outer calorimeter"}, Eur. Phys. J. C57 (2008) 653–663.

\bibitem{HCAL5}
S. Abdullin et al., \emph{"Design, performance, and calibration of CMS hadron endcap calorimeters"}, Europan Journal of Physics C60
(2009) 359–373.

\bibitem{MUON}
  CMS Collaboration,
  \emph{"Muon Technical Design Report"},
  CERN/LHC  97-32 (1997). CMS TDR 3.

\bibitem{TRIGGER1}
  CMS Collaboration,
  \emph{"CMS The TriDAS Project : Technical Design Report, Volume 1: The Trigger Systems"}
   CERN/LHCC-2000-38; CMS TDR 6.1 (2000),  
   \url{https://cds.cern.ch/record/706847/files/cer-002248791.pdf}

\bibitem{TRIGGER2}
  CMS Collaboration,
  \emph{"CMS The TriDAS Project : Technical Design Report, Volume 2: Data Acquisition and High-Level Trigger"}
   CERN-LHCC-2002-026; CMS-TDR-6 (2002), 
   \url{http://cds.cern.ch/record/578006/files/cer-2336481.pdf}
   

\bibitem{COMPUTING}
  CMS Collaboration,
  \emph{"The CMS Computing Model"}, Nuclear Physics B - Proceedings Supplements, Volume 172, October 2007, Pages 53-56.

\bibitem{PF1}  
CMS Collaboration,
\emph{"Particle-Flow Event Reconstruction in CMS and
Performance for Jets, Taus, and MET"}, CMS Physics Analysis Summary
\textbf{PFT-09-001} (2009).

\bibitem{PF2}
CMS Collaboration,
\emph{"Commissioning of the Particle-flow Event
Reconstruction with the first LHC collisions recorded in the CMS detector"},
CMS Physics Analysis Summary
\textbf{PFT-10-001} (2010).

\bibitem{PF3}
CMS Collaboration,
\emph{"Commissioning of the Particle-Flow Reconstruction in
Minimum-Bias and Jet Events from pp Collisions at $\sqrt{s}$ = 7 TeV"},
CMS Physics Analysis Summary
\textbf{PFT-10-002} (2010),
\url{https://cms-physics.web.cern.ch/cms-physics/public/PFT-10-002-pas.pdf}

\bibitem{antikt}
Matteo Cacciari, Gavin P. Salam, Gregory Soyez,
\emph{"The anti-$k_{t}$ jet clustering algorithm"},
JHEP 0804:063, (2008), \eprint{0802.1189}.

\bibitem{fastjet}
Matteo Cacciari, Gavin P. Salam, Gregory Soyez,
\emph{"FastJet user manual"},
The European Physical Journal C 72:1896, arXiv:1111.6097 [hep-ph].  

\bibitem{jetcorrec}
CMS Collaboration,
\emph{"Plans for Jet Energy Corrections at CMS"},
\textbf{CMS PAS JME-07-002}, (2008).

\bibitem{pfjet}
CMS Collaboration,
\emph{"Particle Flow Jet Composition"},
\textbf{CMS AN-2010/005} (2010).    

\bibitem{pileupchs}
CMS Collaboration,
\emph{"Study of Pileup Removal Algorithms for Jets"},
\textbf{CMS PAS JME-14-001} (2014),
\url{https://cds.cern.ch/record/1751454/files/JME-14-001-pas.pdf}

\bibitem{vtagging}
CMS Collaboration,
\emph{"V Tagging Observables and Correlations"},
\textbf{CMS PAS JME-14-002} (2014)

\bibitem{subjetiness}
J. Thaler and K. Van Tilburg,
\emph{"Maximizing Boosted Top Identification by Minimizing
N-subjettiness"},
JHEP 1202 (2012) 093, doi:10.1007/JHEP02(2012)093, arXiv:1108.2701.

\bibitem{softdrop}
A. J. Larkoski, S. Marzani, G. Soyez, and J. Thaler,
\emph{"Soft Drop"},
JHEP 1405 (2014) 146, doi:10.1007/JHEP05(2014)146, arXiv:1402.2657.

\bibitem{pruning}
Stephen D. Ellis, Christopher K. Vermilion, Jonathan R. Walsh
\emph{"Recombination Algorithms and Jet Substructure: Pruning as a Tool for Heavy Particle Searches"},
Phys.Rev.D81:094023,2010, arXiv:0912.0033 [hep-ph].

\bibitem{CaloMET}
CMS Collaboration,
\emph{"Missing $E_{T}$ Performance in CMS"},
CMS Physics Analysis Summary 
\textbf{JME-07-001 (2007)}.

\bibitem{TrackMET}
CMS Collaboration,
\emph{"Track-corrected Missing Transverse Energy in CMS"},
CMS Physics Analysis Summary 
\textbf{JME-09-010 (2009)}.

\bibitem{FiltersMET}
CMS Collaboration,
\emph{"Performance of Missing Transverse Momentum
Reconstruction Algorithms in Proton-Proton Collisions at $\sqrt{s}$ = 8 TeV with the CMS Detector"},
CMS Physics Analysis Summary 
\textbf{CMS-PAS-JME-12-002 } (2012).

\bibitem{TypeIMET}
CMS Collaboration,
\emph{"$\met$ Performance in CMS"},
CMS Analysis Note 
\textbf{CMS AN-2007/041} (2007).

\bibitem{PDG}   
K.A. Olive et al.
\emph{"Particle Data Group"},
Chap 46, KINEMATICS,
Chin. Phys. C, 38, 090001 (2014).

\bibitem{pythia}
T. Sjöstrand, S. Mrenna and P. Skands,
\emph{"A Brief Introduction to PYTHIA 8.1"},
Comput.Phys.Commun. 178, 852-867, (2008) 
\eprint{0710.3820}

\bibitem{madgraph}
J. Alwall, R. Frederix, S. Frixione, V. Hirschi, F. Maltoni, O. Mattelaer, H.-S. Shao, T. Stelzer, P. Torrielli, M. Zaro,
"The automated computation of tree-level and next-to-leading order differential cross sections, and their matching to parton shower simulations",
JHEP07 079 (2014),
\eprint{1405.0301v2}

\bibitem{pat}
W. Adam, V.Adler, B.Hegner, L.Lista, S.Lowette, P.Maksimovic, G. Petrucciani, S.Rappoccio, F.Ronga, R.Tenchini and R.Wolf,
"PAT: The CMS Physics Analysis Toolkit",
J. Phys.: Conf. Ser. 219 032017 doi:10.1088/1742-6596/219/3/032017,
\url{http://iopscience.iop.org/1742-6596/219/3/032017/pdf/1742-6596_219_3_032017.pdf}

\bibitem{jetid}
JME POG (Jet MET Physics Object Group),
\emph{"Jet Identification: Recommendations for 13TeV data analysis"},   
\url{https://twiki.cern.ch/twiki/bin/viewauth/CMS/JetID}   

\bibitem{jetid2}
CMS Collaboration,
\emph{"Performance of the Particle-Flow jet identification criteria
using proton-proton collisions at = 8 TeV"},
\textbf{CMS AN-14-227} (2014)

\bibitem{clean}
CMS Collaboration,
\emph{"PAT Cross Cleaning"},
\url{https://twiki.cern.ch/twiki/bin/view/CMSPublic/SWGuidePATCrossCleaning} 

\bibitem{muonid}
CMS Collaboration,
\emph{"CMS Muon POG"},
\url{https://twiki.cern.ch/twiki/bin/view/CMSPublic/SWGuideMuonId#Loose_Muon.}

\bibitem{muonreco}
CMS Collaboration,
\emph{"Performance of CMS muon reconstruction in pp collision events at $\sqrt{s}$ = 7 TeV"},
JINST 7 P10002 (2012),
\eprint{1206.4071v2}

\bibitem{electronreco}
CMS Collaboration,
"Performance of electron reconstruction and selection with the CMS detector in proton-proton collisions at $\sqrt{s}$= 8 TeV",
JINST 10 P06005 (2015),
\eprint{1502.02701v2}

\bibitem{taureco}
CMS Collaboration,
"Performance of tau-lepton reconstruction and identification in CMS",
JINST 7 P01001 (2012),
\eprint{1109.6034}

\bibitem{HLT}
CMS Collaboration,
\emph{"Instructions for trigger studies"},
\url{https://twiki.cern.ch/twiki/bin/view/CMSPublic/SWGuideTriggerStudiesHowTo}

\bibitem{Trimm} 
David Krohn, Jesse Thaler, and Lian-Tao Wang, 
\emph{"Jet Trimming"},
JHEP 1002:084, (2010), 
\eprint{0912.1342}

\bibitem{Thiagopaper}
CMS Collaboration,
"Search for Randall-Sundrum Gravitons Decaying into
a Jet plus Missing ET at CMS",
CMS Physics Analysis Summary EXO-11-061(2012). \url{http://cdsweb.cern.ch/record/1426654}
 
\bibitem{punzi}
Giovanni Punzi   
\emph{"Sensitivity of searches for new signals and its optimization"},
\eprint{physics/0308063v2}

\bibitem{abcd}
CMS Collaboration,
"Search for Physics Beyond the Standard Model in
Opposite-sign Dilepton Events in pp Collisions at
$\sqrt{s}$ = 7 TeV",
\eprint{1103.1348}

\bibitem{alfametod}
CMS Collaboration,
"Search for new diboson resonances in semileptonic and
hadronic final states at $\sqrt{s}$ = 13 TeV",
CMS AN-15-037 (2015) (Private document)



    
\end{thebibliography}

\end{comment}





\end{document}
